\frb: Properties of VLA Bursts and Implications for Overall FRB Population

### 2016-11-18 repeater-vladata.tex
added note about spectra
added effelsberg filter info. more complete plot with ao obs

% copied from Laura's paper
Observations were conducted at an observing frequency of 4.6 to 5.1~GHz. The S60mm receiver has a system equivalent flux density of 18 Jy and a full-width half-max (FWHM) beam size of 2.4\arcmin at 4.85~GHz. Pulsar search mode data were recorded with the PFFTS backend. Total intensity spectra were recorded with a time resolution of 65.5~$\mu$s and a bandwidth of 500~MHz divided into 128 frequency channels. Note, the inter-channel DM smearing time for 560~pc cm$^{-3}$\ is $\sim$0.2 msec at 4.6 GHz.

@@

@@

>>>>

% copied from Laura's paper
Observations were conducted at an observing frequency of 4.6 to 5.1~GHz. The S60mm receiver has a system equivalent flux density of 18 Jy and a full-width half-max (FWHM) beam size of 2.4\arcmin at 4.85~GHz. Pulsar search mode data were recorded with the PFFTS backend. Total intensity spectra were recorded with a time resolution of 65.5~$\mu$s and a bandwidth of 500~MHz divided into 128 frequency channels. Due to a configuation error, a filter was added that limited the bandwidth to 100-MHz filter centered on 4.85 GHz for Sept 16--18. Note, the inter-channel DM smearing time for 560~pc cm$^{-3}$\ is $\sim$0.2 msec at 4.6 GHz.

@@

Given measured band for VLA/AO detection/limits, plus in-band VLA detections, we can characterize typical burst spectrum as an envelope of width xx MHz. The center frequency can fall at any GHz band.

@@

Given that bursts have $<1$~GHz-scale spectra, wide bandwidths improve odds of detection.
